---
title: "Final_Project_data_read"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(rgeos)
library(geojsonio)
library(extracat)
```

Download the geojson map of NYC from service5.arcgis.com.
Read geojson map and dataset, which can be used by **ggplot::geom_map** and will be printed as following:
```{r}
URL <- "http://services5.arcgis.com/GfwWNkhOj9bNBqoJ/arcgis/rest/services/nycd/FeatureServer/0/query?where=1=1&outFields=*&outSR=4326&f=geojson"
fil <- "nyc_community_districts.geojson"

if (!file.exists(fil)) download.file(URL, fil)

nyc_districts <- geojson_read("nyc_community_districts.geojson", what="sp")
nyc_districts_map <- fortify(nyc_districts, region="BoroCD")
ggplot(data=nyc_districts_map, aes(x=long, y=lat)) +      
  geom_map(map=nyc_districts_map,
                        aes(map_id=id),
                        color="black", 
                        size=0.15, 
                        fill=NA) + 
  coord_map() +
  ggthemes::theme_map()
```

Read in the data from Airbnb (http://insideairbnb.com/get-the-data.html Ver.Sept.19' "Detailed Listings data for New York City"), we are using **read.csv** not **read_csv** for some reason, it will be mentioned later.
```{r}
data = read.csv("listings.csv")
```

##Data Transformation and cleaning

Airbnb provide a gigantic dataset with a great number of variables  
For each housing, it provides information from users' url to the amenity tag to the position(longitude and latitude), etc.

####Remove the data not related to our discussion:  
1. The housing's information (column 1-19):   
descriptions written by the host, which is considered subjective and does not provide a uniform measure on the house.  
2. Hosts' information (col 21-39):   
information about host him/herself:  
3. Common Position (col 42:48):   
Our data downloaded are from NYC database, thus the position description greater than Borough doesn't give any useful information.  
  
And Other column like this, most of the column removed are  
1. **Not related** to our discussion  
2. Give **common information**  
3. There's a good enough statistic in this field  

```{r}
data_cleaned = data[-c(1:19,21:39,42:48,51,60,62:63,68:77,82:86,88:98,100,101,103:105)]
```

####Data cleaning:

**amenities** (The list of amenity string tags) is not converted into a string. for it will be used with a specific API, whose performance is better with factor type.

For all the money value with "$x,xxx.xx" factor format, change it into clean numerical form.
```{r}
data_cleaned$price = as.numeric(gsub(",","",gsub("\\$", "", as.character(data_cleaned$price))))
data_cleaned$security_deposit = as.numeric(gsub(",","",gsub("\\$", "", as.character(data_cleaned$security_deposit))))
data_cleaned$cleaning_fee = as.numeric(gsub(",","",gsub("\\$", "", as.character(data_cleaned$cleaning_fee))))
data_cleaned$extra_people = as.numeric(gsub(",","",gsub("\\$", "", as.character(data_cleaned$extra_people))))
```

The original dataset is too big (in size it's not, but the strings works horrible with R), we write a lighter version out for further studying. All the following research in on this cleaner dataset.
```{r}
write.csv(data_cleaned,'cleaned_nyc_data.csv', row.names=FALSE)
```

##Missing value and missing pattern

For most of the information we need a factor format, we will use **read.csv** rather than **read_csv** here.
As an id, **Host_id** should be a factor rather than numeric, but its factor format will be removed once we re-read the csv, we will re-add it manually everytime..

```{r message=FALSE, warning=FALSE}
df = read.csv('cleaned_nyc_data.csv')
df$host_id = as.factor(df$host_id)
visna(df)
```

Most of the rows are without any missing patterns.

The missing value mainly appear on the following three field:
The house's hardware: **bathrooms**, **bedrooms**,**beds**, rare
Pricing: **security_deposit** and **cleaning_fee** very common
Reviews: The **review_scores_rating** and **reviews_per_month**, common

Common missing patterns:
Missing all the review related (**review_scores_rating** and **reviews_per_month**): the housing may had no visitors before
Missing **security_deposit** only: A lot of hosts actually don't give security depo.
Missing all the pricing related (**security_deposit** and **cleaning_fee**): same idea.
Missing all the review and pricing related: the intersection of the host mentioned above.
Thus the missing pattern is relatively following the common sense, there's no too many missing patterns not following the common sense.
