---
title: "Price Spatial distribution"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rgeos)
library(geojsonio)
library(viridis)
library(dplyr)
```

Download the geojson map of NYC
```{r}
URL <- "http://services5.arcgis.com/GfwWNkhOj9bNBqoJ/arcgis/rest/services/nycd/FeatureServer/0/query?where=1=1&outFields=*&outSR=4326&f=geojson"
fil <- "nyc_community_districts.geojson"

if (!file.exists(fil)) download.file(URL, fil)
```

Read geojson map and dataset
```{r}
nyc_districts <- geojson_read("nyc_community_districts.geojson", what="sp")
nyc_districts_map <- fortify(nyc_districts, region="BoroCD")
df = read_csv('cleaned_nyc_data.csv')
```

###Price distribution

On the price side, for general intuition, check the density

```{r}
ggplot(df, aes(x = price))+
  geom_density()+
  ggtitle("The price distribution")+
  labs(y = "Density", x = "Price")
```

Which gives a extremely right-skewed data, in order to have a practical scale:
check the quantile.

```{r}
Q = unname(df$price %>% quantile())
upper_hinge = Q[4]+(Q[4]-Q[2])*1.5
df_normal = df[df$price < upper_hinge,]
print(upper_hinge)
```

a upper_hinge of 334 looks relatively small with respect to the density curve. Let's check 

```{r}
ggplot(df[df$price > upper_hinge,],aes(x=price))+
  geom_density()+
  ggtitle("price distribution above the upper whisker")
```

```{r}
ggplot(df[df$price >= upper_hinge & df$price <= 2500,],aes(x=price))+
  geom_density()+
  ggtitle("price distribution (zoom in upper whisker to 2500)")
```

```{r}
quantile(df$price,0.99)
```

For a safe and relatively small scale, let's split the distribution into following tags: lower than upper hinge 334, 334-800(99% percentile) and greater than 800 (very expensive, can be considered as somewhat the outlier)

Plot the spatial distribution of housing, try different values, notice 1.the price over 800 may not create large difference. 2. Too large price interval, especially the larger value side will ruin the color scale.
```{r, echo = FALSE}
numericInput("price_distribution_range_min", "Minimum Price", 0,
                 min = 0, max = 10000)
numericInput("price_distribution_range_max", "Maximum Price", 300,
                 min = 0, max = 10000)
```
```{r echo = FALSE, warning=FALSE}
renderPlot({
ggplot(data = df[(df$price >= input$price_distribution_range_min) & (df$price <= input$price_distribution_range_max),c("longitude","latitude","price")],
       aes(x=longitude,y=latitude,color = price))+
   geom_point(size=0.01)+
   scale_color_viridis()+
   geom_map(data=nyc_districts_map, 
            map=nyc_districts_map,
            aes(x=long, y=lat, map_id=id),
            color="black",
            size=0.15, 
            fill=NA) + 
    ggthemes::theme_map()+
    coord_map() +
    ggtitle(paste("Spatial distribution of Airbnb Price, price level $", as.character(input$price_distribution_range_min), " - $", as.character(input$price_distribution_range_max), sep = ""));
})
```

Some conclusion after multiple trys:  
Manhattan and West Brooklyn have most of the expensive housing, no matter what scale is selected. i.e. The distribution of price in these places are more skewed to cheaper side.  
Bronx, Queens generally provide cheap housing (You can easily clarify it by setting minimum price > 200, which will filter out almost every housing in Bronx and Queens)
