---
title: "Final_Project_data_read"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rgeos)
library(geojsonio)
library(viridis)
library(dplyr)
```

Download the geojson map of NYC
```{r}
URL <- "http://services5.arcgis.com/GfwWNkhOj9bNBqoJ/arcgis/rest/services/nycd/FeatureServer/0/query?where=1=1&outFields=*&outSR=4326&f=geojson"
fil <- "nyc_community_districts.geojson"

if (!file.exists(fil)) download.file(URL, fil)
```

Read geojson map and dataset
```{r}
nyc_districts <- geojson_read("nyc_community_districts.geojson", what="sp")
nyc_districts_map <- fortify(nyc_districts, region="BoroCD")
df = read_csv('cleaned_nyc_data.csv')
df$host_id = factor(df$host_id)
ggplot(data=nyc_districts_map, aes(x=long, y=lat)) +      
  geom_map(map=nyc_districts_map,
                        aes(map_id=id),
                        color="black", 
                        size=0.15, 
                        fill=NA) + 
  coord_map() +
  ggthemes::theme_map()
```

###the supply of NYC housing:
####Spatial aspect
First, as all of the data analysis on NYC, let's divide the 
```{r}
ggplot(df, aes(x = neighbourhood_group_cleansed))+
  geom_bar()+
  ggtitle("The Airbnb supply of Sept. 2019")+
  labs(y = "Supply", x = "Borough")
```

For a spacial intuition. Plot the hexagon heatmap supply density on the NYC map:
```{r}
ggplot(df, aes(x = longitude, y = latitude)) +
  geom_hex(bins = 100)+
  scale_fill_viridis()+
  geom_map(data=nyc_districts_map, 
            map=nyc_districts_map,
            aes(x=long, y=lat, map_id=id),
            color="black", 
            size=0.15, 
            fill=NA) + 
  ggthemes::theme_map()+
  ggtitle("Airbnb supply density in NYC")
```

The result follows both the histogram and common sense: Brooklyn and Manhattan provide the most dense supply.

####Host aspect

With calculated_host_listings_count, which is the count of housing provided by this supplier. 

```{r}
ggplot(df, aes(x = calculated_host_listings_count))+
  geom_histogram(binwidth = 1)+
  ggtitle("The Airbnb supply of Sept. 2019")+
  labs(x = "Supply Amount per host")
```

To our surprising, the ratio of host who hosts more than 1 housing is not small at all. At least 30% of the host is offering 2 or more.
```{r}
quantile(df$calculated_host_listings_count,0.70)

```

There's even some "mega-host" in NYC, check by this!
```{r echo = FALSE}
numericInput("large_host_range_min", 
             "The house of host who hosts more than or equal to:", 
             20,
             min = 0, 
             max = 387)
```
```{r, echo = FALSE, Warning = FALSE}
renderPlot({
  ggplot(data = df[(df$calculated_host_listings_count >= input$large_host_range_min), 
                   c("host_id","longitude","latitude")],
         mapping = aes(x=longitude, 
                       y=latitude,
                       color=host_id))+
    geom_point (size=0.1) +
    geom_map(data=nyc_districts_map, 
             map=nyc_districts_map,
             aes(x=long, y=lat, map_id=id),
             color="black", 
             size=0.15, 
             fill=NA) + 
    coord_map() +
    ggthemes::theme_map()+
    theme(legend.position = "none")+
    ggtitle(paste("The Airbnb housing distribution from owner with",
                  as.character(input$large_host_range_min),
                  "housing(s)"
                  ,sep = " "))
  })

```

Let's intuitively have a large host be the one provides greater or equal to 5 housing, who is more likely to be a commercial rather than for-pocket-money one.

```{r}
df = df %>% as_tibble() %>% mutate(
  large_host = ifelse(calculated_host_listings_count >= 5, "Large Host","Small Host")
)
```

```{r, echo = FALSE}
numericInput("distribution_min", 
             "Price range minimum", 
             300,
             min = 0, 
             max = 10000)
numericInput("distribution_max", 
             "Price range maximum", 
             400,
             min = 0, 
             max = 10000)
```
```{r, echo = FALSE}
renderPlot({
ggplot(df[(df$price >= input$distribution_min) & (df$price <= input$distribution_max), c("price","large_host")], aes(x=price, color=large_host)) +
  geom_density(fill="white", alpha=0.5, position="identity")+
  ggtitle("The pricing of large host (>5 housing) vs small host")+
  theme(legend.title = element_blank())
})
```

Generally the large hosts' pricing distribution is same as the small host. (Min = 0, Max = 800)  
Large host provides relativly more extremely cheap (0-50), and relatively expensive(200-400) housing when compared with the small hosts.  




